Digital Analysis of Paintings

### 2014-05-10 paper.tex
Add some conclusions.

This research appears to be of very limited use, but when used within as a part
of a larger system could provide some very interesting analysis which could be
used to train classifiers to detect forgeries, etc. but this still has limited
scope.

@@

\begin{figure}[ht]
\centering
\subfloat[$C=8$]{\includegraphics[width=0.1\textwidth]{dyadic_2.png}}%
\hspace{.2in}%
\subfloat[$C=32$]{\includegraphics[width=0.1\textwidth]{dyadic_4.png}}%
\hspace{.2in}%
\subfloat[$C=128$]{\includegraphics[width=0.1\textwidth]{dyadic_8.png}}%
\hspace{.2in}%
\subfloat[$C=512$ (Original Size)]{\includegraphics[width=0.1\textwidth]{dyadic_16.png}}%
\caption{Example of dyadic space using an image of Grace Hopper (512x512
pixels) at different dyadic scales ($C$), note how the picture becomes less
pixalated at higher scales}
\label{fig:dyadic-image}
\end{figure}

@@

In conclusion this is a very complex but powerful technique which is actually
applying theoretical concepts to perform some interesting analysis and
classification. However, the sensitivity of the technique and with the need for
expert and a posteriori decisions do limit the real application of this
research.

@@

In conclusion this research provides some very powerful analysis with the
experimental results to back it up in two different fields of stylometry which
agree with expert opinion and begin to bring forth some new ideas.

@@

In conclusion this work presents a method which may provide an insight into how
many authors a work has, but has very few experimental results to back up this
claim. Especially given other research into similar areas.

@@

In conclusion, this is a decent application of existing research with real
results being gained, although it doesn't deal with the extraction of
brushstrokes formally it is a good step in the right direction.

@@

In conclusion, this paper presents a very useful method for extracting
brushstrokes and compares the process of doing so to a ground truth. There are
still some elements which could use further investigation, but on the whole
this is a very rounded piece of research.

@@

>>>>

@@

\begin{figure}[ht]
\centering
\subfloat[$C=8$]{\includegraphics[width=0.1\textwidth]{dyadic_2.png}}%
\hspace{.2in}%
\subfloat[$C=32$]{\includegraphics[width=0.1\textwidth]{dyadic_4.png}}%
\hspace{.2in}%
\subfloat[$C=128$]{\includegraphics[width=0.1\textwidth]{dyadic_8.png}}%
\hspace{.2in}%
\subfloat[$C=512$ (Original Size)]{\includegraphics[width=0.1\textwidth]{dyadic_16.png}}%
\caption{Example of dyadic space using an image of Grace Hopper (512x512
pixels) at different dyadic scales ($C$), note how the picture becomes less
pixelated at higher scales}
\label{fig:dyadic-image}
\end{figure}

@@

@@

@@

@@

@@

@@

Digital analysis of artwork is not a trivial task: there are many problems
which occur far more prevalently than in other fields of image processing. The
need for high-resolution copies of artwork with a standard method of capture
can significantly hinder some areas due to the lack of availability.

Added to that, noise is far more common from degradation of works from a lack
of care or poor materials used to create the piece. Although this is a
two-sided coin and there are analysis which could be performed which look at
specific types of degradation to authenticate an artwork.

With all the different kinds of art and materials which can be used to produce
works, it is very difficult not to over specialise in the analysis techniques,
especially when it comes to complex techniques such as detecting brushstrokes.

Texture appears the be the base of a decent analysis technique; most of the
brushstroke extraction technique use some form of texture discrimination to
function. Colour does provide some interesting results, but it is usually the
cumulation of texture and colour which provides the most powerful analysis.
